MSDS6372 - Final Project

### 2018-03-31 MSDS6372_Final_Project_BBHOF.Rmd
Added logisitic regression, and amelia missingness output

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs

@@

# display frequency table for did/did not get inducted into HOF
# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOFRaw$HOFMembership[BBHOFRaw$HOFMembership == 2] <- 1
count(BBHOFRaw, "HOFMembership")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs
library(Amelia) # cool library for exploring missing data

@@

```{r, echo=TRUE, fig.width=8, fig.height=10}
# display missing values
missmap(BBHOFRaw, main="Missing Values in Raw Data")

```{r, echo=TRUE}
# display frequency table for did/did not get inducted into HOF
# since the labels also include 2, converting those to 1, so the result is truly binary (1, 0)
BBHOFRaw$HOFMembership[BBHOFRaw$HOFMembership == 2] <- 1
count(BBHOFRaw, "HOFMembership")

@@

alright....working some logistic regression..

```{r, echo=TRUE}

# copy data set, remove Name from the raw data set, so it's not included in the model, also removing features to play with the model
BBHOF_logistic <- BBHOFRaw
dropcolumns <- c("Name", "StolenBaseRuns", "RunsScored", "OfficialAtBats", "RunsBattedIn", "OnBasePct", "Triples", "StrikeOuts", "AdjustedProduction")
BBHOF_logistic <- BBHOF_logistic[,!(colnames(BBHOF_logistic) %in% dropcolumns)]

# split the raw data into testing and training data
set.seed(101) # set seed so that same sample can be reproduced in future

# now selecting 75% of data as sample from total 'n' rows of the data  
sample <- sample.int(n=nrow(BBHOF_logistic), size=floor(.75*nrow(BBHOF_logistic)), replace=FALSE)

# subset the data using the sample integer vector created above
train <- BBHOF_logistic[sample, ]
test  <- BBHOF_logistic[-sample, ]

# fitting the binomial logistic regression model, HOFMembership is dependent, fitting using all features
model <- glm(train$HOFMembership ~., family=binomial(link='logit'),data=train)

summary(model)
